An Embedding Framework for Consistent Polyhedral Surrogates

### 2021-09-20 poly-embed-journal/poly-embed-journal.tex
5.3

\subsection{Embedding Ordered Partitions via Weston-Watkins Hinge}
\label{sec:winge}
While the hinge loss is the most common surrogate for binary support vector machines (SVMs), original extensions to $n$-class prediction involved a one-vs-all reduction to the binary problem and generating ${n \choose 2}$ hyperplanes via hinge loss.
Proposing a more efficient solution,~\citet*{weston1999support} give an alternate surrogate for multiclass SVM prediction, though originally its consistency with respect to 0-1 loss remained open.
Regardless,~\citet{dogan2016unified} advocate for the Weston-Watkins SVM to be the default for multiclass prediction problems.
The Weston-Watkins hinge loss takes predictions $u \in \reals^n$ and assigns loss
\begin{equation}\label{eq:ww-hinge}
L(u,y) = \sum_{i \in \Y : i \neq y} (1 - (u_y - u_i))_+~.~
\end{equation}

>>>>

\subsection{Embedding Ordered Partitions via Weston-Watkins Hinge}
\label{sec:winge}
As hinge loss is one of the most common surrogates for binary support vector machines (SVMs), original extensions to the multiclass setting involved a one-vs-all reduction to the binary problem via hinge loss, thus generating ${n \choose 2}$ hyperplanes for $n$ labels.
Proposing a more efficient solution,~\citet*{weston1999support} give an alternate surrogate for multiclass SVM prediction, defined as follows for predictions $u \in \reals^n$,
\begin{equation}\label{eq:ww-hinge}
L(u,y) = \sum_{i \in \Y : i \neq y} (1 - (u_y - u_i))_+~.~
\end{equation}
While it was later shown to be inconsistent\raf{Jessie: add cite?}, \citet{dogan2016unified} nonetheless advocate for the Weston-Watkins SVM to be the default for multiclass prediction problems.
